Enhancing diagnostic of stochastic mortality models leveraging contrast trees. An application on Italian data

### 2023-02-23 QuQu/Manuscript Contrast Trees_QuQu.tex
ququ

\documentclass[a4,11pt]{article}
\usepackage[a4paper,left=2.54cm,right=2.54cm,bottom=3cm,top=3cm,text={18cm,20cm},footskip=32pt]{geometry}
\usepackage{latexsym} 	% per i simboli di ogni tipo (numerici, lettrali, caratteri particolari, etc.)
\usepackage{amsmath}  % per la trattazione dei simboli, lettere e gestire il layout delle equazioni matematiche
\usepackage{amsthm}	% per la stilizzazione dei teoremi e per gestire extra simboli matematici, size, space, font, etc..
\usepackage{amsopn}	% per stilizzazione di alcuni operatori matematici (e.g. lim e log)
\usepackage{amscd}	% per gestire frecce e circolarità tramite frecce su più livelli in un'equazione (tipo grafi)
\usepackage{amssymb} % per i simboli matematici
\usepackage{array}	% per creare e gestire array
\usepackage{actuarialsymbol} % per simboli attuariali e di matematica finanziaria 
\usepackage{mathtools} % per integrare amsmath
\usepackage[utf8x]{inputenc} % per encoding language (indispensabile)
\usepackage{makeidx} % per l'indice 
\usepackage{multicol} % per gesttire più colonne nelle tabelle 
\usepackage{multirow} % per gestire più righe nelle tabelle
\usepackage{caption} % per gestire legende e descrizioni di tabelle, grafici e figure
\usepackage{float} % per gestire posizinamento grafici, tabelle e figure varie
\usepackage{enumerate} % pacchetto per le liste numerate 
\usepackage{graphicx} % pacchetto base per inserire i grafici  
\usepackage{subfig} % gestione di figure allineate
\usepackage{booktabs} % per l'ottimizzazione delle tabelle
\usepackage{color}  % gestione di colori delle parole, evidenziare, etc...
\usepackage{colortbl}
\usepackage[english]{babel}  % per la lingua da utilizzare (l'ultima è quella che verrà utilizzata)
\usepackage{wasysym}
\usepackage{appendix} % per inserire appendice
\usepackage{longtable}
\usepackage[numbers]{natbib}
\bibliographystyle{unsrtnat}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{collref}
\usepackage{microtype}  \graphicspath{ {Figures/}} 
\usepackage{lmodern}
\usepackage{soul}
\usepackage{bm}
\usepackage{bookmark}
\usepackage{xcolor}
\usepackage{authblk}

@@

\author[1]{Susanna Levantesi}
\author[1]{Matteo Lizzi}
\author[2*]{Andrea Nigri}

\affil[1]{Department of Statistics, Sapienza University of Rome, Viale Regina Elena 295-G, 00161 Rome, Italy}
\affil[2]{Department of Economics, Management and Territory, University of Foggia, Foggia, Italy} 
\affil[*]{andrea.nigri@unifg.it}
\date{\today}

@@

%-------------------------------------------------------------
\section{Introduction}
%-------------------------------------------------------------
%The life expectancy rise that has occurred in the last decades constitutes a great conquest but contemporarily creates substantial challenges for life insurers and social security schemes providing benefits related to illness, or survival of people. Important policy decisions are based on the human longevity reliable estimates, and public pension policies are a prime example. Thereby, understanding longevity dynamics over age and time is crucial, as they are one of the driving forces of population change. 
\color{red}CITARE \cite{NBL2022} and \cite{Scognamiglio2022}.\color{black}

@@

%-------------------------------------------------------------
\section*{Acknowledgements}
%-------------------------------------------------------------
\color{red}A preliminary version of this paper was presented at the “10th International Conference IES 2022 Innovation \& Society 5.0: Statistical and Economic Methodologies for Quality Assessment”. An extended previous version was published in the Book of short papers of the conference, edited by Rosaria Lombardo, Ida Camminatiello and Violetta Simonacci. \color{black}

>>>>

\documentclass[a4,12pt]{article}
\usepackage[a4paper,left=2.54cm,right=2.54cm,bottom=3cm,top=3cm,text={18cm,20cm},footskip=32pt]{geometry}
\usepackage{latexsym} 	% per i simboli di ogni tipo (numerici, lettrali, caratteri particolari, etc.)
\usepackage{amsmath}  % per la trattazione dei simboli, lettere e gestire il layout delle equazioni matematiche
\usepackage{amsthm}	% per la stilizzazione dei teoremi e per gestire extra simboli matematici, size, space, font, etc..
\usepackage{amsopn}	% per stilizzazione di alcuni operatori matematici (e.g. lim e log)
\usepackage{amscd}	% per gestire frecce e circolarità tramite frecce su più livelli in un'equazione (tipo grafi)
\usepackage{amssymb} % per i simboli matematici
\usepackage{array}	% per creare e gestire array
\usepackage{actuarialsymbol} % per simboli attuariali e di matematica finanziaria 
\usepackage{mathtools} % per integrare amsmath
\usepackage[utf8x]{inputenc} % per encoding language (indispensabile)
\usepackage{makeidx} % per l'indice 
\usepackage{multicol} % per gesttire più colonne nelle tabelle 
\usepackage{multirow} % per gestire più righe nelle tabelle
\usepackage{caption} % per gestire legende e descrizioni di tabelle, grafici e figure
\usepackage{float} % per gestire posizinamento grafici, tabelle e figure varie
\usepackage{enumerate} % pacchetto per le liste numerate 
\usepackage{graphicx} % pacchetto base per inserire i grafici  
\usepackage{subfig} % gestione di figure allineate
\usepackage{booktabs} % per l'ottimizzazione delle tabelle
\usepackage{color}  % gestione di colori delle parole, evidenziare, etc...
\usepackage{colortbl}
\usepackage[english]{babel}  % per la lingua da utilizzare (l'ultima è quella che verrà utilizzata)
\usepackage{wasysym}
\usepackage{appendix} % per inserire appendice
\usepackage{longtable}
\usepackage[numbers]{natbib}
\bibliographystyle{unsrtnat}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{collref}
\usepackage{microtype}  \graphicspath{ {Figures/}} 
\usepackage{lmodern}
\usepackage{soul}
\usepackage{bm}
\usepackage{bookmark}
\usepackage{xcolor}
\usepackage{authblk}

@@

%\author[1]{Susanna Levantesi}
%\author[1]{Matteo Lizzi}
%\author[2*]{Andrea Nigri}

\author[1]{Author 1}
\author[1]{Author 2}
\author[2*]{Author 3}

%\affil[1]{Department of Statistics, Sapienza University of Rome, Viale Regina Elena 295-G, 00161 Rome, Italy}
%\affil[2]{Department of Economics, Management and Territory, University of Foggia, Foggia, Italy} 
%\affil[*]{andrea.nigri@unifg.it}
\affil[1]{Dep. 1}
\affil[2]{Dep. 1}
\affil[*]{authormail}

\date{\today}

@@

%-------------------------------------------------------------
\section{Introduction}
%-------------------------------------------------------------
%The life expectancy rise that has occurred in the last decades constitutes a great conquest but contemporarily creates substantial challenges for life insurers and social security schemes providing benefits related to illness, or survival of people. Important policy decisions are based on the human longevity reliable estimates, and public pension policies are a prime example. Thereby, understanding longevity dynamics over age and time is crucial, as they are one of the driving forces of population change. 
%\color{red}CITARE \cite{NBL2022} and \cite{Scognamiglio2022}.\color{black}

@@

%-------------------------------------------------------------
%\section*{Acknowledgements}
%-------------------------------------------------------------
%A preliminary version of this paper was presented at the “10th International Conference IES 2022 Innovation \& Society 5.0: Statistical and Economic Methodologies for Quality Assessment”. An extended previous version was published in the Book of short papers of the conference, edited by Rosaria Lombardo, Ida Camminatiello and Violetta Simonacci.

%-------------------------------------------------------------
%\section*{Competing Interests}
%-------------------------------------------------------------
%Andrea Nigri, declares that he is a member of the editorial board. However, He does not benefit from the position in the journal at any point during the submission to publication process.
